---
title: "hw04_Ninadh"
author: "Ninadh"
date: "October 15, 2018"
output: html_document
---
```{r}
library(gapminder)
library(tidyverse)
library(ggplot2)
library(knitr)
```

Tabulation of gapminder using knitr

```{r}
gapminder %>%
  knitr::kable()
```

Data reshaping prompts

Task 1: Activity 3, Compute some measure of life expectancy (mean? median? min? max?) for all possible combinations of continent and year.

```{r}
gapminder %>%
  group_by(continent, year) %>%
  summarise(mean = mean(lifeExp), median = median(lifeExp), minimum = min(lifeExp), maximum = max(lifeExp))
```

```{r}
gapminder %>%
  group_by(continent, year) %>%
  summarise(mean = mean(lifeExp), median = median(lifeExp), minimum = min(lifeExp), maximum = max(lifeExp)) %>%
  kable()
```

```{r}
gapminder %>%
  group_by(continent, year) %>%
  summarise(mean = mean(lifeExp), median = median(lifeExp), minimum = min(lifeExp), maximum = max(lifeExp)) %>%
  ggplot(aes(year, mean)) +
  geom_point(aes(colour = continent)) +
  geom_line(aes(colour = continent))
```



```{r}
gapminder %>%
  group_by(continent, year) %>%
  summarise(mean = mean(lifeExp), median = median(lifeExp), minimum = min(lifeExp), maximum = max(lifeExp)) %>%
  ggplot(aes(continent, mean)) +
  geom_bar()
```

The mean life expectancy of Oceania > Europe > Americas > Asia > Africa over time. The life expectancy of Africa is interesting because it plateaued from late 80s to early 2000.


Join Prompts

Task 2: Activity #1

```{r}
WorldPhones
```

```{r}
#number of counties in the continents
continent <- c("Africa", "Asia", "Europe", "Oceania", "Americas")
n_country <- c(54,50,51,25,34)
```

```{r}
data.frame(continent, n_country)
```

```{r}
new_data <- data.frame(continent, n_country)
left_join(gapminder, new_data)
```

```{r}
left_join(gapminder, new_data) %>%
  ggplot(aes(continent, n_country)) +
  geom_point(aes(colour = continent, size = 50))
```





```{r}
left_join(gapminder, new_data) %>%
  ggplot(aes(continent, n_country)) +
  geom_bar()